MRD_final_microbiome

### 2019-06-19 GlobalMicrobiome_NS.Rmd
updated

pseq.cl.rel <- microbiome::transform(clostridium, "compositional")

plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A")

@@

pseq.ph <- aggregate_taxa(pseq, "Phylum")

plot.comp.rel <- plot_composition(pseq.ph.rel, x.label = "sample", plot.type = "heatmap")

plot(plot.comp.rel+ coord_flip()) + theme(axis.text.x=element_blank())
ggsave("phylum_histogram.png")

@@

pseq.n.ph <- aggregate_taxa(pseq.new, "Phylum")

pseq.n.ph.rel <- microbiome::transform(pseq.n.ph, "compositional")

plot.n.comp.rel <- plot_composition(pseq.n.ph.rel, x.label = "sample", plot.type = "heatmap")

p <- plot.n.comp.rel + coord_flip()
p + theme(axis.text.x=element_blank()) + labs(y = "Sample")
ggsave("pnew_histogram.png")

@@

pseq.c.ph <- aggregate_taxa(clostridium, "Phylum")

pseq.c.ph.rel <- microbiome::transform(pseq.c.ph, "compositional")

plot.c.comp.rel <- plot_composition(pseq.c.ph.rel, x.label = "sample", plot.type = "heatmap")

p <- plot.c.comp.rel + coord_flip()
p + theme(axis.text.x=element_blank()) + labs(y = "Sample")
ggsave("clos_histogram.png")

@@

# Plot - Phylum
p.ra.phylum <- ggplot(pseq_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~mnd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum (> 1%)")

@@

@@

# agglomerate at phylum level
clos_phy <- tax_glom(clos, taxrank = "Phylum")

# Transform to rel. abundance (or use ps0.ra)
clos_phyl <- transform_sample_counts(clos_phy, function(x) {x/sum(x)})

# Melt to long format for easy ggploting
clos_phylum <- psmelt(clos_phyl)

# Plot - Phylum
p.ra.phylum <- ggplot(clos_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~mnd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum of Clostridium(> 1%)")

@@

>>>>

pseq.cl.rel <- microbiome::transform(clostridium, "compositional")
#MND
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "mnd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A") 
ggsave("mndcl_relabundance_bar.png")

#PD
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "pd", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A") 
ggsave("pdcl_relabundance_bar.png")

#AD
plot.cl.rel <- plot_composition(pseq.cl.rel, average_by = "ad", x.label = "sample", plot.type = "barplot")
plot.cl.rel + scale_fill_viridis(discrete = TRUE, option = "A") 
ggsave("adcl_relabundance_bar.png")

@@

pseq.ph <- aggregate_taxa(pseq, "Phylum")
pseq.ph.rel <- microbiome::transform(pseq.ph, "compositional")
plot.comp.rel <- plot_composition(pseq.ph.rel, x.label = "sample", plot.type = "heatmap")
plot(plot.comp.rel+ coord_flip()) + theme(axis.text.x=element_blank())
ggsave("phylum_histogram.png")

@@

pseq.n.ph <- aggregate_taxa(pseq.new, "Phylum")
pseq.n.ph.rel <- microbiome::transform(pseq.n.ph, "compositional")
plot.n.comp.rel <- plot_composition(pseq.n.ph.rel, x.label = "sample", plot.type = "heatmap")
p <- plot.n.comp.rel + coord_flip()
p + theme(axis.text.x=element_blank()) + labs(y = "Sample")
ggsave("pnew_histogram.png")

@@

pseq.c.ph <- aggregate_taxa(clostridium, "Phylum")
pseq.c.ph.rel <- microbiome::transform(pseq.c.ph, "compositional")
plot.c.comp.rel <- plot_composition(pseq.c.ph.rel, x.label = "sample", plot.type = "heatmap")
p <- plot.c.comp.rel + coord_flip()
p + theme(axis.text.x=element_blank()) + labs(y = "Sample")
ggsave("clos_histogram.png")

@@

# Plot - Phylum MND
p.ra.phylum <- ggplot(pseq_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~mnd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum (> 1%)")

@@

# Plot - Phylum PD
p.ra.phylum <- ggplot(pseq_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~pd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum (> 1%)")

p <- p.ra.phylum + scale_fill_viridis(discrete = TRUE, option = "A")
plot(p)
ggsave("phylum_abun_pd.png")

# Plot - Phylum AD
p.ra.phylum <- ggplot(pseq_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~ad, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum (> 1%)")

p <- p.ra.phylum + scale_fill_viridis(discrete = TRUE, option = "A")
plot(p)
ggsave("phylum_abun_ad.png")

@@

clos <- aggregate_taxa(clostridium, "Phylum")
# agglomerate at phylum level
clos_phy <- tax_glom(clos, taxrank = "Phylum")                  
# Transform to rel. abundance (or use ps0.ra)
clos_phyl <- transform_sample_counts(clos_phy, function(x) {x/sum(x)}) 
# Melt to long format for easy ggploting
clos_phylum <- psmelt(clos_phyl)

# Plot - Phylum MND
p.ra.phylum <- ggplot(clos_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~mnd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum of Clostridium(> 1%)")

@@

# Plot - Phylum PD
p.ra.phylum <- ggplot(clos_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~pd, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum of Clostridium(> 1%)")

p <- p.ra.phylum + scale_fill_viridis(discrete = TRUE, option = "A")
plot(p)
ggsave("phylum_abun_pd_clos.png")

# Plot - Phylum AD
p.ra.phylum <- ggplot(clos_phylum, aes(x = sample, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", width = 1) +
  facet_wrap(~ad, scales = "free_x", nrow = 4, ncol = 7) +
  theme(axis.text.x = element_blank()) +
  theme(axis.title.x = element_blank()) +
  labs(title = "Abundant Phylum of Clostridium(> 1%)")

p <- p.ra.phylum + scale_fill_viridis(discrete = TRUE, option = "A")
plot(p)
ggsave("phylum_abun_ad_clos.png")
